### 2021-07-30 doc/thesis/chapters/results.tex
create piechart with python

\includepicture [0.75] [0] {Lines of code of the respective system design parts, presented in a pie chart.} {lines_of_code_pie_chart} {img/matlab/lines_of_code_pie_chart}

>>>>

\includepicture [0.75] [0] {Lines of code of the respective system design parts, presented in a pie chart.} {lines_of_code_pie_chart} {img/matlab/lines_of_code_pie_chart_py}
